---
title: "Within-Site-Centering"
author: "Tali Caspi"
date: "2025-06-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages
library(tidyverse); library(brms); library(tidybayes); library(bayesplot); library(DHARMa.helpers); library(DHARMa); library(plotrix); library(parallel); library(coda); library(ggpubr); library(bayestestR); library(ggcorrplot); library(marginaleffects); library(purrr); library(glue)


# Make custom theme
theme_custom <- function() {
  theme_default() +
  theme(panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "white", color = NA),
        plot.title = element_text(size = 7),
        strip.background = element_rect(fill = "grey80", color = NA),
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(size=10),
        axis.title.y = element_text(size=10),
        axis.title.x = element_text(size=10),
        legend.background = element_rect(fill = "white", color = NA))}
```

# Prepare data

This code joins the scat-level ISA values to the hormone and diet data, drops samples collected outside of established coyote territories, and calculates within-territory diet deviations.

```{r}
# Load data frames
hormones_geno <- read.csv("Cleaned_Data/clean_hormone_genotypes_diet.csv")
scat_isa <- read.csv("Cleaned_Data/scat_level_isa.csv")

# Remove scats collected in non-established territories
sites.to.drop <- c("Stern Grove", "Sunset Reservoir")

# Create data frame for GLMM models (all samples with genotypes)
glmm_df <- hormones_geno %>%
  
  # select only relevant data columns
  select(c(SampleID, Individual, Sex, Breeder, Month, Biol.Season, Territory, Condition, Anthropogenic, GC, T3, T4)) %>% 
  
  # add environmental covariates
  left_join(scat_isa, by="SampleID") %>% 
  filter(!Territory %in% sites.to.drop) %>% 
  
  # add within-site centering
  group_by(Territory) %>%
  mutate(Anthro_mean = mean(Anthropogenic, na.rm=TRUE),
         Anthro_within = Anthropogenic - Anthro_mean) %>%
  ungroup()

# make data frame for GC model without the NA from the outlier
glmm_df_GC <- glmm_df %>% filter(SampleID != "S21_0009")
```

# Summary Statistics

```{r}
# Means, SD, and range
glmm_df %>%
  summarize(meanGC = round(mean(GC, na.rm = TRUE), 2),
            sdGC = round(sd(GC, na.rm = TRUE), 2),
            minGC = round(min(GC, na.rm=TRUE),2),
            maxGC = round(max(GC, na.rm=TRUE),5),
            meanT3 = round(mean(T3, na.rm = TRUE), 2),
            sdT3 = round(sd(T3, na.rm = TRUE), 2),
            minT3 = round(min(T3),2),
            maxT3 = round(max(T3),6),
            meanT4 = round(mean(T4, na.rm = TRUE), 2),
            sdT4 = round(sd(T4, na.rm = TRUE), 2),
            minT4 = round(min(T4),2),
            maxT4 = round(max(T4),6)) %>% 
    mutate(across(everything(), ~ sprintf("%.1f", .)))

# Sex table
glmm_df %>% distinct(Individual, Sex) %>% count(Sex) # 34 females, 40 males

# Breeding status table
glmm_df %>% distinct(Individual, Breeder) %>% count(Breeder) # 22 breeders, 52 non-breeders
```

# Construct Models

Use `brms` to fit models. Models include: an interaction between biological season and sex, within-territory centered diet data, breeding status, scat-level impervious surface cover, and condition as fixed effects. Individual and territory are included as random random effects.

```{r}
my.cores <- detectCores()

# GC
glmm_GC_formula <- bf(GC ~ Biol.Season * Sex + scale(Anthro_within) + scale(imperv_prop_500m) + Breeder + Condition + (1 |Individual) + (1|Territory))

mod.GC <- brm(glmm_GC_formula,
                family="lognormal",
                data   = glmm_df_GC, 
                warmup = 2000, iter = 6000, thin=2,
                chains = 4, 
                seed = 666,
                cores  = my.cores,
                control = list(adapt_delta = 0.99, max_treedepth = 15))

# test for interaction of diet with ISA
glmm_GC_formula_int <- bf(GC ~ Biol.Season * Sex + scale(Anthro_within) * scale(imperv_prop_500m) + Breeder + Condition + (1 |Individual) + (1|Territory))

mod.interact <- brm(glmm_GC_formula_int,
                family="lognormal",
                data   = glmm_df_GC, 
                warmup = 2000, iter = 6000, thin=2,
                chains = 4, 
                seed = 666,
                cores  = my.cores,
                control = list(adapt_delta = 0.99, max_treedepth = 15))

# interaction is NOT significant -> move forward with models not including interactive effects

# T3
glmm_T3_formula <- bf(T3 ~ Biol.Season * Sex + scale(Anthro_within) + scale(imperv_prop_500m) + Breeder + Condition + (1 |Individual) + (1|Territory))

mod.T3 <- brm(glmm_T3_formula,
                family="lognormal",
                data   = glmm_df, 
                warmup = 2000, iter = 6000, thin=2,
                chains = 4, 
                seed = 666,
                cores  = my.cores,
                control = list(adapt_delta = 0.99, max_treedepth = 15))

# T4
glmm_T4_formula <- bf(T4 ~ Biol.Season * Sex + scale(Anthro_within) + scale(imperv_prop_500m) + Breeder + Condition + (1 |Individual) + (1|Territory))

mod.T4 <- brm(glmm_T4_formula,
                family="lognormal",
                data   = glmm_df, 
                warmup = 2000, iter = 6000, thin=2,
                chains = 4, 
                seed = 666,
                cores  = my.cores,
                control = list(adapt_delta = 0.99, max_treedepth = 15))

# Save models
saveRDS(mod.GC, "Model_Output/mod.GC.rds")
saveRDS(mod.T3, "Model_Output/mod.T3.rds")
saveRDS(mod.T4, "Model_Output/mod.T4.rds")
saveRDS(mod.interact, "Model_Output/mod.interact.rds")

# Load models
mod.GC <- readRDS("Model_Output/mod.GC.rds")
mod.T3 <- readRDS("Model_Output/mod.T3.rds")
mod.T4 <- readRDS("Model_Output/mod.T4.rds")
```

## Assess model fit

```{r}
# posterior predictive checks
pp_check(mod.GC, ndraws=100)
pp_check(mod.T3, ndraws=100)
pp_check(mod.T4, ndraws=100)

# dharma
dh_check_brms(mod.GC)
dh_check_brms(mod.T3)
dh_check_brms(mod.T4)
```

## Calculate R2

```{r}
r2.GC <- performance::r2_bayes(mod.GC)
r2.T3 <- performance::r2_bayes(mod.T3)
r2.T4 <- performance::r2_bayes(mod.T4)

r2.GC
r2.T3
r2.T4
```

## Extract Model Results

```{r}
models_GLMM <- list(
    mod.GC = mod.GC,
    mod.T3 = mod.T3,
    mod.T4 = mod.T4
  )
  
  # Function to summarize posterior estimates for GLMM models
  summarize_posteriors_glmm <- function(model, model_name) {
    posterior_estimates <- posterior_samples(model) 
    posterior_estimates <- posterior_estimates[, 1:12]
    
    do.call(rbind, lapply(names(posterior_estimates), function(param) {
      values <- posterior_estimates[[param]]
      ci_vals <- bci(values, ci = 0.9)  # toggle sig level as needed
      data.frame(
        Model = model_name,
        Effect = param,
        Estimate = round(mean(values), 4),
        lower = round(ci_vals$CI_low, 4),
        upper = round(ci_vals$CI_high, 4)
      )
    }))
  }
  
  # Loop through all models and combine results for GLMM models
  glmm_results <- do.call(rbind, lapply(names(models_GLMM), function(model_name) {
    summarize_posteriors_glmm(models_GLMM[[model_name]], model_name)
  }))
  
  # Format and pivot results for GLMM models
  glmm_results_clean <- glmm_results %>% 
    group_by(Effect) %>% 
    pivot_wider(
      names_from = Model,
      values_from = c(Estimate, lower, upper))
  
  # Define the custom order for the Effect column
  custom_order <- c(
    "b_Intercept",
    "b_scaleAnthro_within",
    "b_BreederYes",
    "b_Conditionfresh",
    "b_scaleimperv_prop_500m",
    "b_Biol.SeasonMating",
    "b_Biol.SeasonPupping",
    "b_Biol.SeasonMating:SexMale",
    "b_Biol.SeasonPupping:SexMale",
    "b_SexMale",
    "sd_Individual__Intercept",
    "sd_Territory__Intercept")  
  
final_model_results <- glmm_results_clean %>% 
    mutate(Effect = factor(Effect, levels = custom_order)) %>%
    arrange(Effect) %>%
    mutate(
        GC = glue("{round(Estimate_mod.GC, 2)} [{round(lower_mod.GC, 2)}, {round(upper_mod.GC, 2)}]"),
        T3 = glue("{round(Estimate_mod.T3, 2)} [{round(lower_mod.T3, 2)}, {round(upper_mod.T3, 2)}]"),
        T4 = glue("{round(Estimate_mod.T4, 2)} [{round(lower_mod.T4, 2)}, {round(upper_mod.T4, 2)}]")
    ) %>%
    select(Effect, GC, T3, T4)

View(final_model_results)

# write to excel
# write_xlsx(final_model_results, "Model_Output/full_model_results.xlsx")
```

# Repeatability

```{r}

# Variance Components - GC
colnames(posterior_samples(mod.GC))[1:14]

var_ind_GC <- posterior_samples(mod.GC)$"sd_Individual__Intercept"^2
var_terr_GC <- posterior_samples(mod.GC)$"sd_Territory__Intercept"^2
var_res_GC <- (posterior_samples(mod.GC)$"sigma")^2
rpt_ind_GC <- var_ind_GC / (var_ind_GC + + var_terr_GC + var_res_GC)
rpt_terr_GC <- var_terr_GC / (var_ind_GC + + var_terr_GC + var_res_GC)

# Variance Components - T3
var_ind_T3 <- posterior_samples(mod.T3)$"sd_Individual__Intercept"^2
var_terr_T3 <- posterior_samples(mod.T3)$"sd_Territory__Intercept"^2
var_res_T3 <- (posterior_samples(mod.T3)$"sigma")^2
rpt_ind_T3 <- var_ind_T3 / (var_ind_T3 + + var_terr_T3 + var_res_T3)
rpt_terr_T3 <- var_terr_T3 / (var_ind_T3 + + var_terr_T3 + var_res_T3)

# Variance Components - T4
var_ind_T4 <- posterior_samples(mod.T4)$"sd_Individual__Intercept"^2
var_terr_T4 <- posterior_samples(mod.T4)$"sd_Territory__Intercept"^2
var_res_T4 <- (posterior_samples(mod.T4)$"sigma")^2
rpt_ind_T4 <- var_ind_T4 / (var_ind_T4 + + var_terr_T4 + var_res_T4)
rpt_terr_T4 <- var_terr_T4 / (var_ind_T4 + + var_terr_T4 + var_res_T4)

# Repeatability: individual 
mean(rpt_ind_GC);ci(rpt_ind_GC, ci=0.9)
mean(rpt_ind_T3);ci(rpt_ind_T3, ci=0.9)
mean(rpt_ind_T4);ci(rpt_ind_T4, ci=0.9)

# Repeatability: territory
mean(rpt_terr_GC);ci(rpt_terr_GC, ci=0.9) 
mean(rpt_terr_T3);ci(rpt_terr_T3, ci=0.9) 
mean(rpt_terr_T4);ci(rpt_terr_T4, ci=0.9) 
```

# Average Marginal Contrasts and Pairwise Comparisons

Use `avg_comparisons` function in the `marginaleffects` package to calculate average marginal contrasts and corresponding percent differences for each hormone at the following levels:

-   Minimum vs maximum impervious surface area recorded in the study
-   Minimum vs. maximum anthropogenic food recorded in the study (note that these values are within-territory centered and scaled, so they represent deviations)
-   Non-breeders vs. breeders
-   Sexes within each season
-   Seasons within each sex

*Change confidence level as needed between 0.95 and 0.90 to assess significance.*

```{r}
# Calculate observed ranges for ISA and diet covariates
range(glmm_df$imperv_prop_500m) #0.1433071 0.8177232 (14% to 82% impervious cover)
range(glmm_df$Anthro_within) # -0.7065731  0.7727237 (70% less vs. 77% more human food than territory average)

# ============================================================
# FUNCTION: Get percent difference comparisons with 90% CI all non-interactive covariates
# ============================================================
get_ratio_contrast <- function(model, variable, values, label, hormone_name) {
  
  comp <- avg_comparisons(
    model,
    variables = setNames(list(values), variable),
    comparison = "ratio",
    type = "response",
    conf_level = 0.9 # set CI level
  )
  
  data.frame(
    Hormone = hormone_name,
    Covariate = label,
    Estimate = log(comp$estimate),  # put in log scale
    Lower_90 = log(comp$conf.low),
    Upper_90 = log(comp$conf.high),
    Pct_Change = (comp$estimate - 1) * 100, # calc percent change
    Lower_Pct = (comp$conf.low - 1) * 100,
    Upper_Pct = (comp$conf.high - 1) * 100,
     Significant = ifelse(
      sign(comp$conf.low - 1) == sign(comp$conf.high - 1),
      "Yes", "No"))
}

# ============================================================
# FUNCTION: Get percent difference comparisons with 90% CI for pairwise comparisons within interactive effect (Season x Sex)
# ============================================================
get_int_contrasts <- function(model, hormone_name) {
  
  # sex within seasons
  comp_sex <- avg_comparisons(
    model,
    variables = list(
        Sex = c("Female", "Male")),
    by = "Biol.Season",
    comparison = "ratio",
    type = "response", conf_level = 0.9)
  
  sex_contrasts <- data.frame(
    Hormone = hormone_name,
    Covariate = paste0(comp_sex$contrast[1], " (", comp_sex$Biol.Season, ")"),
    Estimate = log(comp_sex$estimate),  # put in log scale
    Lower_90 = log(comp_sex$conf.low),
    Upper_90 = log(comp_sex$conf.high),
    Pct_Change = (comp_sex$estimate - 1) * 100, # calc percent change
    Lower_Pct = (comp_sex$conf.low - 1) * 100,
    Upper_Pct = (comp_sex$conf.high - 1) * 100,
     Significant = ifelse(
      sign(comp_sex$conf.low - 1) == sign(comp_sex$conf.high - 1),
      "Yes", "No"))
  
  # seasons within sex
  comp_season <- avg_comparisons(
  model,
  variables = list(
    Biol.Season = "pairwise"),
  by = "Sex",
  comparison = "ratio",
  type = "response", conf_level = 0.9)
  
  season_contrasts <- data.frame(
    Hormone = hormone_name,
    Covariate = paste0(comp_season$contrast, " (", comp_season$Sex, ")"),
    Estimate = log(comp_season$estimate),  # put in log scale
    Lower_90 = log(comp_season$conf.low),
    Upper_90 = log(comp_season$conf.high),
    Pct_Change = (comp_season$estimate - 1) * 100, # calc percent change
    Lower_Pct = (comp_season$conf.low - 1) * 100,
    Upper_Pct = (comp_season$conf.high - 1) * 100,
     Significant = ifelse(
      sign(comp_season$conf.low - 1) == sign(comp_season$conf.high - 1),
      "Yes", "No"))
  
  return(bind_rows(sex_contrasts, season_contrasts))
}

# ============================================================
# FUNCTION: extract contrasts for all covariates a hormone
# ============================================================
get_all_contrasts_one_hormone <- function(model, hormone_name) {
  
  # Main effects (ISA, Anthropogenic Food, Breeder)
  main_effects <- bind_rows(
    get_ratio_contrast(model, "imperv_prop_500m", c("minmax"), 
                      "ISA", hormone_name),
    get_ratio_contrast(model, "Anthro_within", c("minmax"),
                      "Anthropogenic Food", hormone_name),
    get_ratio_contrast(model, "Breeder", c("No", "Yes"),
                      "Breeder (Yes - No)", hormone_name)
  )
  
  # Season × Sex contrasts
  interaction_effects <- get_int_contrasts(model, hormone_name)
  
  # Combine
  all_contrasts <- bind_rows(main_effects, interaction_effects)
  
  return(all_contrasts)
}

# ============================================================
# Now extract contrasts for all hormones & format table
# ============================================================

all_contrasts <- bind_rows(
  get_all_contrasts_one_hormone(mod.GC, "GC"),
  get_all_contrasts_one_hormone(mod.T3, "T3"),
  get_all_contrasts_one_hormone(mod.T4, "T4")
)


head(all_contrasts)

# format results
formatted_contrasts <-  all_contrasts %>%
  mutate(
    Combined = sprintf("%.2f [%.2f, %.2f]%s\n%.1f%% [%.1f%%, %.1f%%]",
                      Estimate, Lower_90, Upper_90,
                      ifelse(Significant == "Yes", "*", ""),
                      Pct_Change, Lower_Pct, Upper_Pct)
  ) %>%
  select(Covariate, Hormone, Combined) %>%
  pivot_wider(names_from = Hormone, values_from = Combined)

head(formatted_contrasts)

# save as excel file
# write_xlsx(formatted_contrasts, "Model_Output/all_contrasts.xlsx")
```

# Plots

## Within-Territory Effects of Diet

```{r}
# Get main conditional effects for Anthro_within (population-level)
cond_GC_ID <- conditional_effects(mod.GC, effects = "Anthro_within", prob=0.9)
cond_GC_ID <- data.frame(cond_GC_ID$Anthro_within)

cond_T3_ID <- conditional_effects(mod.T3, effects = "Anthro_within", prob=0.9)
cond_T3_ID <- data.frame(cond_T3_ID$Anthro_within)

cond_T4_ID <- conditional_effects(mod.T4, effects = "Anthro_within", prob=0.9)
cond_T4_ID <- data.frame(cond_T4_ID$Anthro_within)


# Plot
p.GC.within <- ggplot() +
  # Raw data points and lines
  geom_point(data = glmm_df_GC, aes(x = Anthro_within, y = log(GC), group = Territory), alpha = 0.5, color="grey") +
  
  geom_smooth(data = glmm_df_GC, aes(x = Anthro_within, y = log(GC), group = Territory), color="grey", alpha = 0.7, size = 0.8, method="lm", se=F) +
  
  # Population-level model estimated effect line + ribbon
  geom_ribbon(data = cond_GC_ID, aes(x = Anthro_within, ymin = log(lower__), ymax = log(upper__)), fill = "#CC7677", alpha = 0.3) +
  geom_line(data = cond_GC_ID, aes(x = Anthro_within, y = log(estimate__)), color = "#A4193D", size = 1.5, linetype="dashed") +
  # Graphics
  labs(
    x = NULL,
    y = "Log Glucocorticoids (ng/g)") +
  scale_x_continuous(expand = c(0.001, 0.01), breaks=c(-0.5,0,0.5)) +
  scale_y_continuous(limits = c(1.5, 7.2), breaks = c(2, 3, 4, 5, 6, 7))+
  theme_custom()

# Plot
p.T3.within <- ggplot() +
  # Raw data points and lines
  geom_point(data = glmm_df, aes(x = Anthro_within, y = log(T3), group = Territory), alpha = 0.5, color="grey") +
  
  geom_smooth(data = glmm_df, aes(x = Anthro_within, y = log(T3), group = Territory), color="grey", alpha = 0.7, size = 0.8, method="lm", se=F) +
  
  # Population-level model estimated effect line + ribbon
  geom_ribbon(data = cond_T3_ID, aes(x = Anthro_within, ymin = log(lower__), ymax = log(upper__)), fill = "#FFA15D", alpha = 0.3) +
  geom_line(data = cond_T3_ID, aes(x = Anthro_within, y = log(estimate__)), color = "#FF7522", size = 1.5) +
  # Graphics
  labs(
    x = NULL,
    y = "Log Triiodothyronine (ng/g)") +
  scale_x_continuous(expand = c(0.001, 0.01),breaks=c(-0.5,0,0.5)) +
  scale_y_continuous(limits = c(1.5, 7.2), breaks = c(2, 3, 4, 5, 6, 7))+
  theme_custom()

# Plot
p.T4.within <- ggplot() +
  # Raw data points and lines
  geom_point(data = glmm_df, aes(x = Anthro_within, y = log(T4), group = Territory), alpha = 0.5, color="grey") +
  
  geom_smooth(data = glmm_df, aes(x = Anthro_within, y = log(T4), group = Territory), color="grey", alpha = 0.7, size = 0.8, method="lm", se=F) +
  
  # Population-level model estimated effect line + ribbon
  geom_ribbon(data = cond_T4_ID, aes(x = Anthro_within, ymin = log(lower__), ymax = log(upper__)), fill = "#55C235", alpha = 0.3) +
  geom_line(data = cond_T4_ID, aes(x = Anthro_within, y = log(estimate__)), color = "#2D661C", size = 1.5) +
  # Graphics
  labs(
    x = "Proportion Anthropogenic Food \n (Within-Territory Centered)",
    y = "Log Thyroxine (ng/g)") +
  scale_x_continuous(expand = c(0.001, 0.01), breaks=c(-0.5,0,0.5)) +
  scale_y_continuous(limits = c(1.5, 7.2), breaks = c(2, 3, 4, 5, 6, 7))+
  theme_custom()

ggarrange(p.GC.within, p.T3.within, p.T4.within, nrow = 3, align = "hv")
```

## Impervious surface cover

```{r}
# Define a sequence of values for ISA from 0 to 100
ISA_values <- seq(0, 1, by = 0.01) 
int_conditions <- list(imperv_prop_500m = ISA_values)

cond_GC_ISA <- conditional_effects(mod.GC, effects = "imperv_prop_500m", int_conditions = int_conditions, prob=0.9)
cond_GC_ISA <- data.frame(cond_GC_ISA$imperv_prop_500m)

cond_T3_ISA <- conditional_effects(mod.T3, effects = "imperv_prop_500m", int_conditions = int_conditions, prob=0.9)
cond_T3_ISA <- data.frame(cond_T3_ISA$imperv_prop_500m)

cond_T4_ISA <- conditional_effects(mod.T4, effects = "imperv_prop_500m", int_conditions = int_conditions, prob=0.9)
cond_T4_ISA <- data.frame(cond_T4_ISA$imperv_prop_500m)

# Plot
p.GC.ISA <- ggplot() +
  
  # Raw data points and lines
  geom_point(data = glmm_df_GC, aes(x = imperv_prop_500m, y = log(GC), group = Territory), alpha = 0.5, color="grey") +
  
  # Population-level model estimated effect line + ribbon
  geom_ribbon(data = cond_GC_ISA, aes(x = imperv_prop_500m, ymin = log(lower__), ymax = log(upper__)), fill = "#CC7677", alpha = 0.3) +
  geom_line(data = cond_GC_ISA, aes(x = imperv_prop_500m, y = log(estimate__)), color = "#A4193D", size = 1.5, linetype="solid") +
  # Graphics
  labs(
    x = NULL,
    y = "Log Glucocorticoids (ng/g)") +
  scale_x_continuous(expand = c(0.001, 0.01)) +
  scale_y_continuous(limits = c(1.5, 7.2), breaks = c(2, 3, 4, 5, 6, 7))+
  theme_custom()

p.T3.ISA <- ggplot() +
  # Raw data points and lines
  geom_point(data = glmm_df, aes(x = imperv_prop_500m, y = log(T3), group = Territory), alpha = 0.5, color="grey") +
  # Population-level model estimated effect line + ribbon
  geom_ribbon(data = cond_T3_ISA, aes(x = imperv_prop_500m, ymin = log(lower__), ymax = log(upper__)), fill = "#FFA15D", alpha = 0.3) +
  geom_line(data = cond_T3_ISA, aes(x = imperv_prop_500m, y = log(estimate__)), color = "#FF7522", size = 1.5, linetype="solid") +
  # Graphics
  labs(
    x = NULL,
    y = "Log Triiodothyronine (ng/g)") +
  scale_x_continuous(expand = c(0.001, 0.01)) +
  scale_y_continuous(limits = c(1.5, 7.2), breaks = c(2, 3, 4, 5, 6, 7))+
  theme_custom()

# Plot
p.T4.ISA <- ggplot() +
  # Raw data points and lines
  geom_point(data = glmm_df, aes(x = imperv_prop_500m, y = log(T4), group = Territory), alpha = 0.5, color="grey") +
  # Population-level model estimated effect line + ribbon
  geom_ribbon(data = cond_T4_ISA, aes(x = imperv_prop_500m, ymin = log(lower__), ymax = log(upper__)), fill = "#55C235", alpha = 0.3) +
  geom_line(data = cond_T4_ISA, aes(x = imperv_prop_500m, y = log(estimate__)), color = "#2D661C", size = 1.5, linetype="solid") +
  # Graphics
  labs(
    x = "Proportion Impervious Surface Cover \n",
    y = "Log Thyroxine (ng/g)") +
  scale_x_continuous(expand = c(0.001, 0.01)) +
  scale_y_continuous(limits = c(1.5, 7.2), breaks = c(2, 3, 4, 5, 6, 7))+
  theme_custom()

ggarrange(p.GC.ISA, p.T3.ISA, p.T4.ISA, nrow = 3, align = "hv")
```

## Arrange all continuous effect plots

```{r}
ggarrange(p.GC.within, p.GC.ISA, 
          p.T3.within, p.T3.ISA,
          p.T4.within, p.T4.ISA,
          ncol=2, nrow=3,
          labels = c("a", "d", "b", "e", "c", "f"),
          label.x = 0.14)

# ggsave("Figures/all_cont_var.png", dpi=600, height=7, width=6)
```

## Categorical Effects: Breeding Status and Sex x Season

```{r}
# Extract conditional effects
cond_breeder_GC_ID <- conditional_effects(mod.GC, effects="Breeder", prob=0.9)
cond_breeder_T3_ID <- conditional_effects(mod.T3, effects="Breeder", prob=0.9)
cond_breeder_T4_ID <- conditional_effects(mod.T4, effects="Breeder", prob=0.9)

cond_breeder_GC_ID <- data.frame(cond_breeder_GC_ID$Breeder)
cond_breeder_T3_ID <- data.frame(cond_breeder_T3_ID$Breeder)
cond_breeder_T4_ID <- data.frame(cond_breeder_T4_ID$Breeder)

p.GC_breeder <- ggplot(cond_breeder_GC_ID, 
                             aes(x = Breeder, y = log(estimate__),
                                             group=Breeder, fill=Breeder)) +
  
  # add raw data
  geom_jitter(data = glmm_df_GC, aes(x = Breeder, y = log(GC), color=Breeder), 
              alpha = 0.5, size=1, width=0.2)+
  
  # plot conditional estimates and SE
  geom_point(size = 3, shape=21, color="black") +
  geom_errorbar(aes(ymin = log(lower__), ymax = log(upper__)), 
                width = 0.05, size = 0.5)+
    # Graphics
  xlab(NULL) +
  ylab("Log Glucocorticoids (ng/g)") +
  theme_custom() +
  scale_fill_manual(values=c("#A4193D", "#CC7677"))+
  scale_color_manual(values=c("#A4193D", "#CC7677"))+
  scale_y_continuous(limits = c(1.5, 7.5), breaks = c(2, 3, 4, 5, 6, 7)) +
   scale_x_discrete(labels = c("Yes" = "Breeding", "No" = "Non-Breeding"))+
  theme(legend.position = "none")

p.T3_breeder <- ggplot(cond_breeder_T3_ID, 
                             aes(x = Breeder, y = log(estimate__),
                                             group=Breeder, fill=Breeder)) +
  
  # add raw data
  geom_jitter(data = glmm_df, aes(x = Breeder, y = log(T3), color=Breeder), 
              alpha = 0.5, size=1, width=0.2)+
  
  # plot conditional estimates and SE
  geom_point(size = 3, shape=21, color="black") +
  geom_errorbar(aes(ymin = log(lower__), ymax = log(upper__)), 
                width = 0.05, size = 0.5)+
    # Graphics
  xlab(NULL) +
  ylab("Log Triiodothyronine (ng/g)") +
  theme_custom() +
  scale_fill_manual(values=c("#FF7522", "#ffb27d"))+
  scale_color_manual(values=c("#FF7522", "#ffb27d"))+
  scale_y_continuous(limits = c(1.5, 7.5), breaks = c(2, 3, 4, 5, 6, 7)) +
   scale_x_discrete(labels = c("Yes" = "Breeding", "No" = "Non-Breeding"))+
  theme(legend.position = "none")


p.T4_breeder <- ggplot(cond_breeder_T4_ID, 
                             aes(x = Breeder, y = log(estimate__),
                                             group=Breeder, fill=Breeder)) +
  
  # add raw data
  geom_jitter(data = glmm_df, aes(x = Breeder, y = log(T4), color=Breeder), 
              alpha = 0.5, size=1, width=0.2)+
  
  # plot conditional estimates and SE
  geom_point(size = 3, shape=21, color="black") +
  geom_errorbar(aes(ymin = log(lower__), ymax = log(upper__)), 
                width = 0.05, size = 0.5)+
    # Graphics
  xlab(NULL) +
  ylab("Log Thyroxine (ng/g)") +
  theme_custom() +
  scale_fill_manual(values=c("#2D661C", "#55C235"))+
  scale_color_manual(values=c("#2D661C", "#55C235"))+
  scale_y_continuous(limits = c(1.5, 7.5), breaks = c(2, 3, 4, 5, 6, 7)) +
   scale_x_discrete(labels = c("Yes" = "Breeding", "No" = "Non-Breeding"))+
  theme(legend.position = "none")


### SEX BY SEASON ###

cond_GC_ID_month.sex <- conditional_effects(mod.GC, prob=0.9)[7]
cond_GC_ID_month.sex <- data.frame(cond_GC_ID_month.sex$`Biol.Season:Sex`)
cond_T3_ID_month.sex <- conditional_effects(mod.T3, prob=0.9)[7]
cond_T3_ID_month.sex <- data.frame(cond_T3_ID_month.sex$`Biol.Season:Sex`)
cond_T4_ID_month.sex <- conditional_effects(mod.T4, prob=0.9)[7]
cond_T4_ID_month.sex <- data.frame(cond_T4_ID_month.sex$`Biol.Season:Sex`)

# GC
p.GC.int <- ggplot(cond_GC_ID_month.sex, 
                         aes(x = Biol.Season, y = log(estimate__), 
                             group = Sex, fill = Sex)) + 
    # Add raw data
    geom_jitter(data = glmm_df_GC, aes(x = Biol.Season, y = log(GC), 
                                        color = Sex),  alpha = 0.5, size=1, 
        position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.4)) +
    
    # Plot conditional estimates and SE
    geom_point(size = 3, shape = 21, color = "black", 
               position = position_dodge(width = 0.4)) +
    geom_errorbar(aes(ymin = log(lower__), ymax = log(upper__)), 
                  width = 0.05, size = 0.5, 
                  position = position_dodge(width = 0.4)) +
    
    # Graphics
    xlab(NULL) +
    ylab("Log Glucocorticoids (ng/g)") +
    theme_custom() +
    scale_fill_manual(values = c("#A4193D", "#CC7677")) +
    scale_color_manual(values = c("#A4193D", "#CC7677")) +
    scale_y_continuous(limits = c(1.5, 7.5), breaks = c(2, 3, 4, 5, 6, 7)) +
    theme(legend.position = "none")

# T3
p.T3.int <- ggplot(cond_T3_ID_month.sex, 
                         aes(x = Biol.Season, y = log(estimate__), 
                             group = Sex, fill = Sex)) + 
    # Add raw data
    geom_jitter(data = glmm_df, aes(x = Biol.Season, y = log(T3), 
                                        color = Sex),  alpha = 0.5, size=1, 
        position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.4)) +
    
    # Plot conditional estimates and SE
    geom_point(size = 3, shape = 21, color = "black", 
               position = position_dodge(width = 0.4)) +
    geom_errorbar(aes(ymin = log(lower__), ymax = log(upper__)), 
                  width = 0.05, size = 0.5, 
                  position = position_dodge(width = 0.4)) +
    
    # Graphics
    xlab(NULL) +
    ylab("Log Triiodothyronine (ng/g)") +
    theme_custom() +
    scale_fill_manual(values = c("#FF7522", "#ffb27d")) +
    scale_color_manual(values = c("#FF7522", "#ffb27d")) +
    scale_y_continuous(limits = c(1.5, 7.5), breaks = c(2, 3, 4, 5, 6, 7)) +
    theme(legend.position = "none")

# T4
p.T4.int <- ggplot(cond_T4_ID_month.sex, 
                         aes(x = Biol.Season, y = log(estimate__), 
                             group = Sex, fill = Sex)) + 
    # Add raw data
    geom_jitter(data = glmm_df, aes(x = Biol.Season, y = log(T4), 
                                        color = Sex),  alpha = 0.5, size=1, 
        position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.4)) +
    
    # Plot conditional estimates and SE
    geom_point(size = 3, shape = 21, color = "black", 
               position = position_dodge(width = 0.4)) +
    geom_errorbar(aes(ymin = log(lower__), ymax = log(upper__)), 
                  width = 0.05, size = 0.5, 
                  position = position_dodge(width = 0.4)) +
    
    # Graphics
    xlab(NULL) +
    ylab("Log Thyroxine (ng/g)") +
    theme_custom() +
    scale_fill_manual(values = c("#2D661C", "#55C235")) +
    scale_color_manual(values = c("#2D661C", "#55C235")) +
    scale_y_continuous(limits = c(1.5, 7.5), breaks = c(2, 3, 4, 5, 6, 7)) +
    theme(legend.position = "none")

  
## Arrange Plots ##
ggarrange(p.GC_breeder, p.T3_breeder, p.T4_breeder,
          p.GC.int, p.T3.int, p.T4.int, nrow=2, ncol=3,
          labels = c("a", "b", "c", "d", "e", "f"),
          label.x = 0.16)

# ggsave("Figures/categorical.png", dpi=600, height=5, width=8)
```
