---
title: "ISA_coyscat_buffers"
output: html_document
date: "2026-01-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf); library(terra); library(tidyverse); library(mapview); library(tigris)
```

**Load in coordinates and create buffers**

```{r}
# load coordinates
coords <- read.csv("Cleaned_Data/clean_hormone_genotypes_diet.csv") %>% 
  select(SampleID, Lat, Long)

# Convert to sf object
pts <- st_as_sf(coords, coords = c("Long", "Lat"), crs = 4326)

mapview(pts) # check

# transform to UTM
pts_proj <- st_transform(pts, "EPSG:32611")

# take a look at it again
mapview(pts_proj)
st_crs(pts_proj) # check out our projection system 

# create buffers
buffer_500m <- st_buffer(pts_proj, dist = 500)
buffer_1km <- st_buffer(pts_proj, dist = 1000)

mapview(buffer_500m, col.regions="grey80")
mapview(buffer_1km, col.regions="grey80")
```

**Load in impervious surface raster, crop to SF, and reproject**

You must download the impervious surface raster from here: <https://www.mrlc.gov/data>. Download the 2021 Fractional Impervious Surface (CONUS) and save it on your own computer.

```{r}
# get land boundary
sf_county <- counties(state = "CA", year = 2020) %>%
  filter(NAME == "San Francisco" | NAME == "San Mateo") %>%
  st_transform(32611)

mapview(sf_county) # check

# get water areas
sf_water <- area_water(state = "CA", county = c("San Francisco", "San Mateo", "Marin"), year = 2020) %>%
  st_transform(32611)

mapview(sf_water) # check

# load impervious surface area raster - replace with string to file on your own computer
imperv_rast <- rast("../../../Postdoc/GitHub_Projects/bayarea-spatial-data/Data/Annual_NLCD_FctImp_2021_CU_C1V1/Annual_NLCD_FctImp_2021_CU_C1V1.tif")

# create a bounding box around 1km buffers for cropping ISA raster
bbox_buffers <- st_bbox(buffer_1km) %>%
  st_as_sfc() %>%
  st_buffer(1000)

# transform bbox to raster's CRS
bbox_raster_crs <- st_transform(bbox_buffers, crs(imperv_rast))

# crop raster to size of bbox
imperv_crop <- crop(imperv_rast, vect(bbox_raster_crs))

# reproject cropped raster to match buffers
imperv_utm <- project(imperv_crop, "EPSG:32611", method = "bilinear")

plot(imperv_utm) # check
```

**Create masks to remove water from impervious surface area raster**

```{r}
# rasterize water polygons such that water pixels = 1, land pixels = NA
water_vect <- vect(sf_water)
water_rast <- rasterize(water_vect, imperv_utm)

plot(water_rast) # check that water pixels are colored and land is not

# create land mask such that land pixels = 1, water pixels = NA
land_mask <- ifel(is.na(water_rast), 1, NA)

plot(land_mask) # check that land pixels are colors and water is not

# Mask impervious surface to land only: land pixels keep their ISA values, water pixels become NA
imperv_land <- imperv_utm * land_mask

plot(imperv_land) # check
```

**Calculate proportion of impervious surface area in each buffer**

```{r}
# write function to calculate mean impervious proportion
calc_imperv_prop <- function(buffer_sf, raster, id_col) {
  results <- data.frame(
    SampleID = buffer_sf[[id_col]],
    imperv_prop = NA,
    total_land_pixels = NA,
    mean_imperv_pct = NA,
    stringsAsFactors = FALSE
  )
  
  for (i in 1:nrow(buffer_sf)) {
    # Extract raster values within buffer
    buf_vect <- vect(buffer_sf[i, ])
    vals <- terra::extract(raster, buf_vect, fun = NULL, ID = FALSE)[[1]]
    
    # Remove NA values (water areas)
    vals_land <- vals[!is.na(vals)]
    
    if (length(vals_land) > 0) {
      # Calculate mean impervious surface
      # NLCD values are 0-100 representing percent impervious
      results$total_land_pixels[i] <- length(vals_land)
      results$mean_imperv_pct[i] <- mean(vals_land)
      results$imperv_prop[i] <- mean(vals_land) / 100  # Convert to 0-1 proportion
    }
  }
  
  return(results)
}

# calculate impervious proportions for both buffer sizes
results_500m <- calc_imperv_prop(buffer_500m, imperv_land, id_col = "SampleID")
results_1km <- calc_imperv_prop(buffer_1km, imperv_land, id_col = "SampleID")

# rename columns based on buffer size
names(results_500m)[2] <- "imperv_prop_500m"
names(results_500m)[4] <- "mean_imperv_pct_500m"
names(results_1km)[2] <- "imperv_prop_1km"
names(results_1km)[4] <- "mean_imperv_pct_1km"

# combine results
final_results <- buffer_500m %>%
  st_drop_geometry() %>%
  select(SampleID) %>%
  left_join(results_500m %>% select(SampleID, imperv_prop_500m, mean_imperv_pct_500m), by = "SampleID") %>%
  left_join(results_1km %>% select(SampleID, imperv_prop_1km, mean_imperv_pct_1km), by = "SampleID")

head(final_results) # check

# write.csv(final_results, "Cleaned_Data/scat_level_isa.csv", row.names = F)

# summarize ranges/means per territory

summary_isa <- read.csv("Cleaned_Data/clean_hormone_genotypes_diet.csv") %>% 
  select(SampleID, Territory) %>% 
  left_join(final_results) %>% 
  group_by(Territory) %>% 
  summarize(
    min_500m = min(mean_imperv_pct_500m),
    max_500m = max(mean_imperv_pct_500m),
    mean_500m = mean(mean_imperv_pct_500m),
    min_1km = min(mean_imperv_pct_1km),
    max_1km = max(mean_imperv_pct_1km),
    mean_1km = mean(mean_imperv_pct_1km)
  )

summary_isa
```
